---
title: "ADS2 Mock Coding Challenge 2"
date: "Semester 2, 2023-24"
output: pdf_document
---

```{r, include=FALSE}
library(tidyverse)
```

time 
```{r}
Sys.time()
```


# Treatment for type 1 diabetes (T1D)

Your team developed an insulinomimetic that can be used to substitute insulin in patients with T1D. You induced T1D in mice by injecting them with streptozotocin (this drug destroys pancreatic $/beta$/-cells, which abrogates insulin production and leads to the loss of control over glucose metabolism). Subsequently, mice were injected with vehicle or this novel drug in 2 possible concentrations. Their blood glucose level (mM) was measured before the injection and 1 hour after.

Answer the questions below and provide clear and reproducible code as well as your comments.

## Import, check, and organize the data appropriately. Treat data and reformat columns if needed.

import and view
```{r}
data <-read.csv("t1d_drug.csv")
head(data, 10)
```
summary
```{r}
summary(data)
```
check NA and duplicate
```{r}
anyNA(data)
anyDuplicated(data)
```
find NA
```{r}
head(subset(data, Comment == "Died" & Measurement == "Glucose_after"))
```
remove died mouse
```{r}
data_no_died <- subset(data, Comment != "Died")
```
turn to the longer
```{r}
data_analysis <- data_no_died %>% pivot_wider(names_from = Measurement, values_from = Glucose) %>% select(!Comment)

data_analysis$Diff <- data_analysis$Glucose_before-data_analysis$Glucose_after
```

## Plot the data in a useful way.
```{r}
p1 <- ggplot(data_no_died)
p2 <- p1 + geom_boxplot(aes(x=Treatment, y=Glucose, fill=Measurement))
p2
```

## Choose, justify, state the statistical hypotheses, and carry out an appropriate test to answer whether the drug is useful.
use ANOVA
```{r}
model <- aov(Diff~Treatment, data_analysis)
```
  -H0:
  -H1:
assumption test
maybe use plot to judge. QQ for normal, 
```{r, eval}
par(mfrow = c(1, 4))
plot(model)
```
three: random and independent, normal distribution of reseidual, homogeneity of variance
```{r}
shapiro.test(resid(model))
```
```{r}
bartlett.test(Diff~Treatment, data_analysis)
```
anova result analysis
```{r}
summary(model)
```
```{r}
TukeyHSD(model)
```

## Present and discuss your results. Is this novel drug useful? What would you suggest doing next?
useful
power estimate
