---
title: "ADS2 Coding Challenge 1 - Mock paper"
author: ""
date: "`r format(Sys.time(), '%c')`" 
output: 
  pdf_document: 
    latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      tidy = T,
                      tidy.opts = list(width.cutoff = 60),
                      fig.width = 10, 
                      fig.height = 5,
                      cache = T)
```

# 1. Stroop test

## Import the data and plot them in a useful way.

```{r}
strp_test <- read.csv("stroop_test.csv")
library(ggplot2)
strp_plot <- ggplot(data = strp_test, 
                    mapping = aes(x = Time, y = Score, group = Time))
strp_plot + geom_boxplot(aes(fill = Time)) 
```

## Is there a difference in performance on the Stroop task between the morning and afternoon group?

```{r}
mean(strp_test$Score)
strp_morning <- subset(strp_test, Time == "Morning")
mean(strp_morning$Score)
strp_afternoon <- subset(strp_test, Time == "Afternoon")
mean(strp_afternoon$Score)
```

```{r}
t.test(sample(strp_morning$Score, 10), 
       sample(strp_afternoon$Score, 10))
```

## Name one way in which the study could be improved or followed up on.

more participants?

\newpage

# 2. Marathon finishing times

## Import the dataset, and plot it in a way that addresses the question we are interested in.

```{r}
mrt_time <- read.csv("Chicago2013_random_finishers.csv")
mrt_plot <- ggplot(data = mrt_time)
mrt_plot + geom_boxplot(aes(x = Gender, y = Time))
```

```{r}
mrt_plot + geom_col(aes(x = Age, y = Time, fill = Gender))
```

```{r}
q <- ggplot(mrt_time, aes(x=Age,y=Time, col=Gender))
q <- q+xlab("Age") + ylab("Time [hours]")
q <- q + geom_point(size = 3)
q
```

## What are the average finishing times and standard deviation for each gender? What are the average finishing times and standard deviation for each age quartile?

```{r}
mrt_M <- subset(mrt_time, Gender == "M")
mean(mrt_M$Time)
sd(mrt_M$Time)
mrt_F <- subset(mrt_time, Gender == "F")
mean(mrt_F$Time)
sd((mrt_F$Time))
```

## If you had to suggest a statistical test to determine the effect of age quartile and gender on marathon finishing time, what test would you suggest, and why?

```{r}
```

\newpage

# 3. Antiviral drug

## What are the Null Hypothesis and the Alternative Hypothesis in Prof. Liu's trial?

1.  Null: no differences in the recovery time between two group of mouses. $H_0$
2.  Alternative: the recovery time of two group of mouses is different.

## For her statistical analysis, Prof. Liu uses the commonly used significance level $\alpha$ of $0.05$. What type of error does this relate to, and how?

1.  This related to type I error
2.  Type I error means rejecting null hypothesis when it is true. The significance level $\alpha$ of $0.05$ means that when rejecting the null hypothesis, there is still 5% probability that null hypothesis is true.

## After ensuring that the sample size is big enough and that the assumptions of the statistical tests are met, Prof. Liu runs a statistical test and gets a p-value of $0.059$. What is a p-value? Based on this result, what should Prof. Liu report as the outcome of this study?

1.  P-value is the probability of obtaining results at least as extreme as the observed results of a statistical hypothesis test.
2.  P-value = 0.059 \> 0.05 means there is no difference(null hypothesis).
